Using Scipion for Stream Image Processing at EM Facilities

### 2018-04-02 3.workflow.tex
almost there switty

 %\item \emph{Ume\aa\ Core Facility for Electron Microscopy} (UCEM, \url{http://www.kbc.umu.se/english/ucem})[** Jose Miguel can you verify this?] 
 \item \emph{Science for life Laboratory} (SciLifeLab, \url{http://www.scilifelab.se}). Both at Stockholm and Ume\aa\ facilities)
 \item \emph{ESRF Cryo-Electron Microscope} (\url{http://www.esrf.eu/home/UsersAndScience/Experiments/MX/About_our_beamlines/CM01.html})
 \item \emph{eBIC at Diamond Light Source} ( \url{http://www.diamond.ac.uk/Science/Integrated-facilities/eBIC.html})
 \item \emph{CNB CryoEM Service} (\url{http://www.cnb.csic.es/index.php/en/research/core-facilities/microscopia-crioelectronica})
 \item \emph{Molecular Microscopy Consortium - NIH} (\url{https://www.niehs.nih.gov/research/atniehs/facilities/mmc/index.cfm})[**Pablo can you confirm this?]
 \item \emph{National Cancer Institute - NIH} (\url{https://cmm.nci.nih.gov/})[**Pablo can you confirm this?]

@@

\subsection{\scipion near future}
%Particle picking
%Extract particle
%2D classify (either classes or identify outliers)
%Initial model
%More complex reports
plug-in style, independend

>>>>

 %\item \emph{Ume\aa\ Core Facility for Electron Microscopy} (UCEM, \url{http://www.kbc.umu.se/english/ucem})[** Jose Miguel can you verify this?] 
 \item \emph{The Swedish National Cryo-EM Facility}. The Facility has two nodes: at \scilifelab in Stockholm and at Ume\aa\ University (\url{http://www.scilifelab.se}, \url{http://www.kbc.umu.se/english/ucem/cryo-em/})
 \item \emph{ESRF Cryo-Electron Microscope} (\url{http://www.esrf.eu/home/UsersAndScience/Experiments/MX/About_our_beamlines/CM01.html})
 \item \emph{eBIC at Diamond Light Source} ( \url{http://www.diamond.ac.uk/Science/Integrated-facilities/eBIC.html})
 \item \emph{CNB CryoEM Service} (\url{http://www.cnb.csic.es/index.php/en/research/core-facilities/microscopia-crioelectronica})
 \item \emph{Molecular Microscopy Consortium - NIH} (\url{https://www.niehs.nih.gov/research/atniehs/facilities/mmc/index.cfm})[**Pablo can you confirm this?]
 \item \emph{National Cancer Institute - NIH} (\url{https://cmm.nci.nih.gov/})[**Pablo can you confirm this?]

@@

### 2018-04-02 3.workflow_diamond.tex
almost there switty

\subsection{The eBIC facility at Diamond Light Source}

Diamond Light Source is the UK National Synchrotron User Facility.  As such, it provides access to large-scale experimental facilities to the UK and worldwide scientific communities to conduct experiments that are not possible in their home laboratories.  As a consequence of this national role, Diamond has significant experience at managing many visiting scientists and user experiments, and the associated data and post-processing.  %In the area of Macromolecular Crystallography, this has become a highly automated process which allows users to visualise electron density maps within minutes of the experiment being completed (REF. Aller P et al Methods Mol Biol 2015)
%The recent ``Revolution Resolution'' (REF. Kulbrandt W, Science 2014) in cryoEM has transformed the impact and demand of cryoEM in Structural Biology. However, the instrumentation and running costs of the latest generation of EM necessary for high-end cryoEM is beyond scope of all but the best-funded home laboratories. Due to the huge demand for high-end microscope access, 
The electron Bio-Imaging Centre (eBIC) was set up at Diamond~\citep{diamond2017}. The centre houses four Thermofisher Titan Krios, a Talos Arctica and a Scios dual-beam. All of the transmission electron microscopes are equipped with counting-mode direct electron detectors and Volta phase plates.

@@

Data is collected onto a local machine %in a similar way to the CNB setup, but 
and then immediately moved via 10Gbps Ethernet to the associated visit directory in the centralised storage, a multi Petabyte GPFS High Performance Parallel file system.  Once the raw data is present on the GPFS system, high speed interconnects to the central cluster enable rapid data processing. %Services such as these are shared amongst the whole facility allowing for flexibility in their deployment and generally allowing better service.

Once the data has reached the central file system, it is available to be processed by Scipion.  This process is facilitated by the use of a Scipion-workflow-template which enable novice users to trigger semi-customised on the fly processing. This template consists of a small UI (figure XX) which allows the user to put in the specific values pertinent to their experiment, namely the session ID (or visit number), which microscope they are using, and several other key data collection parameters.  Once set this makes use of a global template for Scipion as set up by the eBIC team, and substitutes the appropriate information into it, and then saves it to disk.

Following this Diamond makes use of a central ActiveMQ [** what is this? a queue system] service which is triggered upon the template file being available in the visit directory, and runs a headless (i.e. without UI) version of Scipion which takes the template and executes in streaming mode.  THIS SHOULD PROBABLY INCLUDE SOMETHING ABOUT THE DETECTION OF NEW FILES BY SOCKET MESSAGE, BUT I DON’T KNOW HOW THIS WORKS. Me neither, I thought it polled the filesystem?

To monitor the progress of the automatic processes, the Scipion pipeline at Diamond also includes custom nodes which allow it to interface with ISPyB.  This provides the users with a web interface showing general metadata about their experiment as well as new real-time updates on steps of the process and relevant output such as motion corrected images, drift values and CTF images (Figure XXX)

>>>>

\subsection{Case 3: Scipion at eBIC facility (Diamond Light Source)}

Diamond Light Source is the UK National Synchrotron User Facility.  As such, it provides access to large-scale experimental facilities to the UK and worldwide scientific communities to conduct experiments that are not possible in their home laboratories.  As a consequence of this national role, Diamond has significant experience at managing many visiting scientists and user experiments, and the associated data and post-processing.  %In the area of Macromolecular Crystallography, this has become a highly automated process which allows users to visualise electron density maps within minutes of the experiment being completed (REF. Aller P et al Methods Mol Biol 2015)
%The recent ``Revolution Resolution'' (REF. Kulbrandt W, Science 2014) in cryoEM has transformed the impact and demand of cryoEM in Structural Biology. However, the instrumentation and running costs of the latest generation of EM necessary for high-end cryoEM is beyond scope of all but the best-funded home laboratories. Due to the huge demand for high-end microscope access, 
Recently, the electron Bio-Imaging Centre (eBIC) has been set up at Diamond~\citep{diamond2017}. The centre houses four Thermofisher Titan Krios, a Talos Arctica and a Scios dual-beam. All of the transmission electron microscopes are equipped with counting-mode direct electron detectors and Volta phase plates.

\subsubsection{Network Setup and IT Infrastructure}

@@

Data is collected onto a local machine %in a similar way to the CNB setup, but 
and then immediately moved via 10Gbps Ethernet to the associated visit directory in the centralized storage, a multi Petabyte GPFS high performance parallel file system.  Once the raw data is present on the GPFS system, high speed interconnects to the central cluster enable rapid data processing. %Services such as these are shared amongst the whole facility allowing for flexibility in their deployment and generally allowing better service.

Diamond IT infrastructure is complex and requires to integrate a large collection of heterogeneous systems. In this environment a major problem is to achieve interaction and data exchange between diverse applications. One of the solutions to this problem has been to implement \emph{indirect communication} through a message queuing system. Simply said; a message queuing system is a software where queues can be defined, applications may connect to the queue and send or retrieve  messages. A message can include any kind of information, for example, about a process/task that should start on another application (that could be on another server). %The message queuing software stores the messages until a receiving application connects and takes a message off the queue. The receiving application then processes the message in an appropriate manner.

\subsection{Additional Software Developments: ISyB monitor, Scipion Headless}

From the image processing point of view, in Diamond, a typical cryoEM session starts by launching a custom made script that performs two actions. First, it  allows users to specify values pertinent to their experiment, namely the session ID (or visit number), which microscope they are using, and several other key data collection parameters. Once set, a workflow file is created and then saved to disk.
The file creation triggers the message system \emph{ActiveMQ} and a ``file creation'' message is created. The second action performed by the custom made script is to start a \scipion instance in the microscope control computer.
The instance runs in headless mode. \scipion headless mode has been developed specifically for eBIC and allows \scipion to be executed without user interface in large clusters with no graphical board.

%(a) script: (1) create workflow, (2) launchs headless scipion
%(b) scipion starts webservice [knows nothing about the queue]
%(c) second script (name please) (running all the time?) ask activeMQ for messages
%    speaks with import movies [decuple Scipion from ActiveMQ], more generic solution

After \scipion is launched the \protocol{import movie} protocol starts. \protocol{Import movie} needs to look for a list of files on the file system with names matching a pattern but, in Diamond distributed file system, this is a very expensive task. Therefore, \protocol{import movie} has been modified so it opens a webservice that waits until an auxiliary script connects to \emph{ActiveMQ}, retrieves all the  messages reporting creation of new files than satisfy the search pattern and reports the actual filenames. It would have been possible to suppress the auxiliary script and make \protocol{import movie} access directly to \emph{ActiveMQ} but we decided against this solution because we did not want to incorporate in \scipion code valid for a single facility. In this way, all code that is related with Diamond's IT infrastructure is encapsulated in the auxiliary script.

To monitor the progress of the automatic image processing CNB and \scilifelab cryo-EM services make use of \scipion default monitor system. In Diamond, the electronic notebook ISPyB is the standard tool to record and show metadata about the different experiments. In this way, a new monitor has been developed which, through a webservice, allows \scipion to directly interface with ISPyB.  This setup provides the users with a web interface showing general metadata about their experiment as well as  real-time updates on steps of the process and relevant output such as motion corrected images, drift values, CTF images, etc.

Although most of developments described in this subsection will be integrated in the main \scipion code repository at present they are available in a developer's branch  at \url{https://github.com/I2PC/scipion/tree/release-1.1-headless-devel}.

### 2018-04-02 3.workflow_scilifelab.tex
almost there switty

\subsection{Case 2: Scipion at SciLifeLab}

The Swedish National Cryo-EM Facility offers access to state-of-the-art equipment and expertise in single particle cryo-EM and cryo electron tomography (cryo-ET). The Facility has two nodes: at SciLifeLab in Stockholm and at Ume\aa\ University. SciLifeLab in Stockholm offers single-particle service with a 
Talos Arctica for sample optimisation and a Titan Krios for high-resolution data collection. The Ume\aa\ node is expected to become operational during 2018, and will offer cryo-ET with a Titan Krios and a Scios DualBeam SEM.

@@

At the beginning of 2016, the Cryo-EM facility at SciLifeLab became one of the early adopters of \scipion for on the fly data processing. Before, there were some home-made scripts to perform motion correction (with motioncorr) and CTF estimation (with Gctf) but the microscope operators recognized the importance of a more general framework. In particular, they were interested in the possibility of modify easily the processing workflow as well as provide users and staff with  graphical tools for data analysis and quick feedback regarding the data collection. Initially, the same setup script used at CNB was adopted, but it did not fully satisfy the facility requirements and a new one has been developed. In the following sections we will briefly describe the computational infrastructure at the SciLifeLab node at Stockholm and the implementation of a Session Wizard to automate the initial setup while fetching information from other sources external to \scipion. 
[** thalos falcon III, titan k2 and falcon III]

\subsubsection{Network Setup and IT Infrastructure}
At the heart of the SciLifeLab computational infrastructure is a storage and pre-processing server (the
staging server). This machine has roughly 200 TB of storage (4 ZFS RAIDZ2 pools
with 11 HDDs each), 2 NVIDIA GeForce GTX 1070 GPUs, 2 Intel Xeon E5-2630v4 CPUs
(10 cores, 2.2 GHz, HT), 384 GB RAM, and a dual-port 10 GbE network card. The
storage pool is exported via NFS and Samba, so the microscope computers can
write data there directly and other machines can access it.

Unfortunately, the K2 [** Jose Miguel, what is K2?, do you have 2 cameras? in the same microscope or in different ones, this is confusing, comment when ] computer writes data to a local SSD RAID while the Falcon-III does it to a dedicated storage server. %, in order to avoid interruption of data collection due to network issues. 
So when users start the data collection, they launch a script that continuously moves the produced data to the staging server.

%ata on the staging server, in an organized folder structure, we
%can run pre-processing directly on the server.] If data processing is started soon
%after data collection the incoming data file should be in RAM-cache and  no
%disk access in needed, which is important with performance in mind. 
After processing, users can copy their data to external USB drives from two workstations in the
microscope room that have access to the storage pool via NFS.
There is also a dedicated download server which have access to the NFS export. This download server 
can be reached though the Internet and allow downloads via rsync (over SSH) or SFTP.

@@

\subsubsection{Additional Software Developments: \emph{Session Wizard}}
In order to interface \scipion with the microscope infrastructure an upgraded version of the original script developed at the CNB was used. Unfortunately, it was difficult to reuse the existing code due to a different folder structure and, more important, a different logic about users and microscopes management. To address the new set of requirements, a new wizard is under development at SciLifeLab. For this new wizard, a basic data model was designed representing the current processing and data organization at SciLifeLab. The model is composed by the following entities:

[** quitar modelo de datos]
\begin{itemize}
\setlength\itemsep{0em}
 \item \textit{User}: represents all persons that can book microscope time or are registered in the Application Portal 
 related to national projects.
 \item \textit{Reservation}:  is a resource (e.g, Krios, Talos, Vitrobot, etc) booking for a given period of time.
 \item \textit{Order}:  is a given national project with an unique identifier in the Application Portal
 \item \textit{Project}:  can be a either a national project (related to a given Order) or an internal project.
 \item \textit{Session}:  stores information about the usage of the micrograph for a given day.
\end{itemize}

When an user starts a data collection, the wizard is also executed using the command \textit{session-titan} (or \textit{session-talos}). The wizard will fetch the reservations for this day using the webservice API provided by the Booking System [** chanr booking system by the official name] and will check which user is operating the microscope. From the reservation information, the wizard will also detect if it is an internal or a national facility project. If the latter, more information will be retrieved from the Application Portal (such as principal investigator, project code, contact person or invoice address). After gathering all this information, the wizard will store this information, create the processing environment and launch \scipion. %For example, the movies-import protocol will already point to the location where the files will be written for this session. Moreover, taking into account which microscope-camera is being  used, the files pattern can be inferred.

@@

The described session wizard can be found at  \url{https://github.com/delarosatrevin/scipion-session}. It has been design to satisfy SciLifeLab requirements and, although readers are welcomed to try it, no support is offered.

%existing data model represents the specify usage at the SciLifeLab facility and there are not immediate plans to make it more general and easy to reuse. Nonetheless, the model is quite simple and should to be difficult to modify it to fit other requirements.

>>>>

\subsection{Case 2: Scipion at The Swedish National Cryo-EM Facility}

The Swedish National Cryo-EM Facility offers access to state-of-the-art equipment and expertise in single particle cryo-EM and cryo electron tomography (cryo-ET). The Facility has two nodes: at \scilifelab in Stockholm and at Ume\aa\ University. \scilifelab in Stockholm offers single-particle service with a 
Talos Arctica for sample optimisation and a Titan Krios for high-resolution data collection. The Ume\aa\ node is expected to become operational during 2018, and will offer cryo-ET with a Titan Krios and a Scios DualBeam SEM.

@@

At the beginning of 2016, the Cryo-EM facility at \scilifelab became one of the early adopters of \scipion for on the fly data processing. Before, there were some home-made scripts to perform motion correction (with motioncorr) and CTF estimation (with Gctf) but the microscope operators recognized the importance of a more general framework. In particular, they were interested in the possibility of modify easily the processing workflow as well as provide users and staff with  graphical tools for data analysis and quick feedback regarding the data collection. Initially, the same setup script used at CNB was adopted, but it did not fully satisfy the facility requirements and a new one has been developed. In the following sections we will briefly describe the computational infrastructure at the \scilifelab node and the implementation of a Session Wizard to automate the initial setup while fetching information from other sources external to \scipion. 
%[** thalos falcon III, titan k2 and falcon III]

\subsubsection{Network Setup and IT Infrastructure}
At the heart of the \scilifelab computational infrastructure there is a storage and pre-processing server (the staging server). This machine has roughly 200 TB of storage (4 ZFS RAIDZ2 pools with 11 HDDs each), 2 NVIDIA GeForce GTX 1070 GPUs, 2 Intel Xeon E5-2630v4 CPUs (10 cores, 2.2 GHz, HT), 384 GB RAM, and a dual-port 10 GbE network card. The storage pool is exported via NFS and Samba, so the microscope computers can write data there directly and other machines can access it.
%Unfortunately, the K2 [** Jose Miguel, what is K2?, do you have 2 cameras? in the same microscope or in different ones, this is confusing, comment when ] computer writes data to a local SSD RAID while the Falcon-III does it to a dedicated storage server. %, in order to avoid interruption of data collection due to network issues.

In order to avoid interruption of data collection due to network issues each microscope has their own dedicated storage, that in the case of the Titan microscope is double since it may be connected to two different cameras, a K2 and a Falcon III.  In this way, after starting the data collection, users launch a script that continuously moves the produced data from the adequate storage to the staging server.

%ata on the staging server, in an organized folder structure, we
%can run pre-processing directly on the server.] If data processing is started soon
%after data collection the incoming data file should be in RAM-cache and  no
%disk access in needed, which is important with performance in mind. 
After processing, users may  copy their data to external USB drives from two workstations in the microscope room that have access to the storage pool via NFS.
There is also a dedicated download server which have access to the NFS export. This download server can be reached though the Internet and allow downloads via rsync (over SSH) or SFTP.

@@

\subsubsection{Additional Software Developments: \emph{Session Wizard}}
In order to interface \scipion with the microscope infrastructure an upgraded version of the original script developed at the CNB was used. Unfortunately, it was difficult to reuse the existing code due to a different folder structure and, more important, a different logic about users and microscopes management. To address the new set of requirements, a new wizard is under development at \scilifelab. For this new wizard, a basic data model was designed representing the current processing and data organization at \scilifelab. %The model is composed by the following entities:

%[** quitar modelo de datos]
%\begin{itemize}
%\setlength\itemsep{0em}
% \item \textit{User}: represents all persons that can book microscope time or are registered in the Application Portal 
% related to national projects.
% \item \textit{Reservation}:  is a resource (e.g, Krios, Talos, Vitrobot, etc) booking for a given period of time.
% \item \textit{Order}:  is a given national project with an unique identifier in the Application Portal
% \item \textit{Project}:  can be a either a national project (related to a given Order) or an internal project.
% \item \textit{Session}:  stores information about the usage of the micrograph for a given day.
%\end{itemize}

When an user starts a data collection, the wizard is also executed using the command \textit{session-titan} (or \textit{session-talos}). The wizard will fetch the reservations for this day using the webservice API provided by \emph{Booked Scheduler} and will check which user is operating the microscope. From the reservation information, the wizard will also detect if it is an internal or a national facility project. If the latter, more information will be retrieved from the Application Portal (such as principal investigator, project code, contact person or invoice address). After gathering all this information, the wizard will store this information, create the processing environment and launch \scipion. %For example, the movies-import protocol will already point to the location where the files will be written for this session. Moreover, taking into account which microscope-camera is being  used, the files pattern can be inferred.

@@

The described session wizard can be found at  \url{https://github.com/delarosatrevin/scipion-session}. It has been design to satisfy \scilifelab requirements and, although readers are welcomed to try it, no support is offered.

%existing data model represents the specify usage at the \scilifelab facility and there are not immediate plans to make it more general and easy to reuse. Nonetheless, the model is quite simple and should to be difficult to modify it to fit other requirements.

### 2018-04-02 5.conclusions.tex
go home
almost there switty

\scipion is provided 
freely as open source software. Online documentation
describing \scipion download and installation is available
at \url{http://scipion.cnb.csic.es/m/download_form/} and \url{https://github.com/I2PC/scipion/wiki/How-to-Install}, respectively. Cloud installation instruction are available at \url{https://github.com/I2PC/scipion/wiki/Scipion-in-the-Cloud}. Other public software mentioned in this article as \emadmin, \emadmin and \emph{wizard session} are available at \url{https://github.com/rmarabini/webservices/tree/master/EMadmin} and \url{\url{https://github.com/delarosatrevin/scipion-session}} respectively.
If you would like more information about how to install \scipion or you have suggestions on how to improve it contact us at scipion@cnb.csic.es.

>>>>

\scipion is provided 
freely as open source software. Online documentation
describing \scipion download and installation is available
at \url{http://scipion.cnb.csic.es/m/download_form/} and \url{https://github.com/I2PC/scipion/wiki/How-to-Install}, respectively. Cloud installation instruction are available at \url{https://github.com/I2PC/scipion/wiki/Scipion-in-the-Cloud}. Other public software mentioned in this article as \emadmin, \emph{wizard session} and the different scripts used at eBIC are available at \url{https://github.com/rmarabini/webservices/tree/master/EMadmin}, \url{\url{https://github.com/delarosatrevin/scipion-session}} and \url{https://github.com/I2PC/scipion/tree/release-1.1-headless-devel} respectively.
If you would like to have more information about how to install \scipion or you have suggestions on how to improve it contact us at scipion@cnb.csic.es.

### 2018-04-02 6.acknowledgments.tex
almost there switty

----------------

    AFTER THIS LINE I JUST SAVED SOME TEXT THAT MAY BE USEFUL IN THE FUTURE DISREGARD THIS MATERIAL

    --------------------

\section{Project stability and funding}

Scipion development is been done in the context of the Instruct Image Processing Cen-
ter (I2PC, http://i2pc.cnb.csic.es). Instruct is the European initiative for Strategic
Scientific Infrastructures (ESFRI) for Structural Biology. The I2PC started with the objective 
to provide efficient support for research projects in Europe demanding expertise in 
electron microscopy image processing. In order to support a large collection
of projects, the first activities of the I2PC were oriented to design and implement the
necessary software tools.

At present the I2PC has this money and this people

ScipionBox is part of the Scipion package which is provided 
freely as open source software. Online documentation
describing Scipion download and installation is available
at \url{http://scipion.cnb.csic.es/m/download_form/} and \url{https://github.com/I2PC/scipion/wiki/How-to-Install}, respectively.

%It was recognized the need for a platform that could provide
%a friendly GUI on top of advanced image processing algorithms and, at the same time,
%assure standardization, traceability and reproducibility.
\section{Things to mention if possible}
\begin{itemize}
 \item Cloud
\end{itemize}

>>>>

%\section{Project stability and funding}

%Scipion development is been done in the context of the Instruct Image Processing Cen-
%ter (I2PC, http://i2pc.cnb.csic.es). Instruct is the European initiative for Strategic
%Scientific Infrastructures (ESFRI) for Structural Biology. The I2PC started with the objective 
%to provide efficient support for research projects in Europe demanding expertise in 
%electron microscopy image processing. In order to support a large collection
%of projects, the first activities of the I2PC were oriented to design and implement the
%necessary software tools.

%At present the I2PC has this money and this people

%ScipionBox is part of the Scipion package which is provided 
%freely as open source software. Online documentation
%describing Scipion download and installation is available
%at \url{http://scipion.cnb.csic.es/m/download_form/} and \url{https://github.com/I2PC/scipion/wiki/How-to-Install}, respectively.

%It was recognized the need for a platform that could provide
%a friendly GUI on top of advanced image processing algorithms and, at the same time,
%assure standardization, traceability and reproducibility.
%\section{Things to mention if possible}
%\begin{itemize}
% \item Cloud
%\end{itemize}

### 2018-04-02 scipionbox.tex
almost there switty

%\usepackage{lineno}
\usepackage[update,prepend]{epstopdf}
%\linenumbers
\definecolor{lightgreen}{rgb}{0.75,0.75,0.0}
%\usepackage{caption}
%\usepackage{endfloat}
%\DeclareCaptionFormat{empty}{}
%\captionsetup{format=empty}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot[R]{\footnotesize  \thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\def\scipionbox{\textit{ScipionBox}\xspace}
\def\scipion{\textit{Scipion}\xspace}
\def\emadmin{\textit{EMAdmin}\xspace}
\def\epu{\textit{EPU}\xspace}
\newcommand{\protocol}[1]{\texttt{#1}}

@@

\begin{document}
\title{Using Scipion for Stream Image Processing at EM Facilities}
\author{Scipion Boys$^{(a)}$,\\
Jos\'e Miguel de la Rosa-Trev\'{i}n$^{(c)}$,\\
Marta Carroni$^{(c)}$,\\
Stefan Fleichman$^{(c)}$,\\
Erik Lindahl$^{(c,d)}$\\
Ashton AW$^{(e)}$,\\
Basham M$^{(e)}$,\\
Clare DK$^{(e)}$,\\
Savage K$^{(e)}$,\\
Siebert CA$^{(e)}$,\\
        }

@@

\newpage
\input{0.abstract.tex}
\input{1.introduction.tex}
\input{2.overall.tex}
\input{3.workflow.tex}
\input{4.results.tex}
\input{5.conclusions.tex}
\input{6.acknowledgments.tex}
\appendix

>>>>

%\usepackage{lineno}
\usepackage[update,prepend]{epstopdf}
%\linenumbers
\definecolor{lightgreen}{rgb}{0.75,0.75,0.0}
%\usepackage{caption}
%\usepackage{endfloat}
%\DeclareCaptionFormat{empty}{}
%\captionsetup{format=empty}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot[R]{\footnotesize  \thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\def\scipionbox{\textit{ScipionBox}\xspace}
\def\scipion{\textit{Scipion}\xspace}
\def\emadmin{\textit{EMAdmin}\xspace}
\def\epu{\textit{EPU}\xspace}
\def\scilifelab{SciLifeLab\xspace}
\newcommand{\protocol}[1]{\texttt{#1}}

@@

\begin{document}
\title{Using Scipion for Stream Image Processing at EM Facilities}
Authors to be sorted later
\author{C.O.S. Sorzano$^{(a)}$,
A. Jim\'{e}nez$^{(a)}$,
R. Melero$^{(a)}$,\\
M. Mart\'{i}nez$^{(a)}$,
J. G\'{o}mez-Blanco$^{(a)}$,
L. del Cano$^{(a)}$,\\
T. Majtner$^{(a)}$,
E. Ram\'{i}rez$^{(a)}$,
P. Conesa$^{(a)}$,\\
J.L. Vilas$^{(a)}$,
R. Marabini$^{(a)}$,
Y. Rancel$^{(a)}$,
J.M. Carazo$^{(a)}$,\\
J.M. de la Rosa-Trev\'{i}n$^{(c)}$,
M. Carroni$^{(c)}$,
S. Fleichman $^{(c)}$,\\
E. Lindahl$^{(c,d)}$
A.W. Ashton$^{(e)}$,
M. Basham$^{(e)}$,\\
D.K. Clare$^{(e)}$,
K. Savage$^{(e)}$,
C.A. Siebert$^{(e)}$,\\
D. Maluenda$^{(a)}$
        }

@@

\newpage
\input{0.abstract.tex}
\input{1.introduction.tex}
\input{2.overall.tex}
\input{3.workflow.tex}
\input{4.future.tex}
\input{5.conclusions.tex}
\input{6.acknowledgments.tex}
\appendix
